# LabCase projects per project type analysis

```{r warning=FALSE, message=FALSE}

# Load libraries
library(dplyr)
library(magrittr)
library(lubridate)

library(xtable)
library(yaml)
library(RODBC)

library(ggplot2)
library(RColorBrewer)
library(grid)


config <- yaml.load_file('../config.yml')



```

Data as of  **`r as.character(now())`**


## Overview

This report shows the number of created LabCase projects grouped by project type. For this analysis project type is either `internal` or `external`. 

We visualize the grouped projects within several different time spans using bar plots.


## Data extraction and pre-processing




```{r}


connect <- odbcConnect('LabCase', uid=config$odbc$uid, pwd=config$odbc$pwd)

query <- 'SELECT p.id, p.identifier, p.name, p.created_on, 
            p.is_public, p.project_size, p.template_project_id, 
            p.last_updated_on, COUNT(m.user_id) AS member_count
            FROM projects AS p
            LEFT OUTER JOIN members AS m
            ON p.id = m.project_id
            GROUP BY p.id;'
projects <- sqlQuery(connect, query=query)

# Extract custom field information
# In the LC database this is the relevant id - custom fields mapping:
# 12: Use as template
# 13: Customer
# 14: Country
# 15: Business Line
query <- 'SELECT p.id, c.custom_field_id AS cf_id, c.value AS cf_value
            FROM projects AS p
            INNER JOIN custom_values AS c
            ON
            p.id = c.customized_id
            WHERE 
            c.custom_field_id IN (12,13,14,15) 
            AND c.customized_type = \"Project\"'
custom_fields <- sqlQuery(connect, query=query)

close(connect)



projects <- filter(custom_fields, cf_id == 12) %>%
  select(id, cf_value) %>%
  droplevels %>%
  rename(template = cf_value) %>%
  left_join(projects, ., by = 'id')

# Extract project id and customer information from custom_fields data frame
#  id:       project id
#  cf_value: customer name
# In the LC database this is the relevant id - custom fields mapping:
#   13: Customer
projects <- filter(custom_fields, cf_id == 13) %>%
  select(id, cf_value) %>%
  droplevels %>%
  rename(customer = cf_value) %>%
  left_join(projects, ., by = 'id')

# Extract project id and country information from custom_fields data frame
#  id:       project id
#  cf_value: country name
# In the LC database this is the relevant id - custom fields mapping:
#   14: Country
projects <- filter(custom_fields, cf_id == 14) %>%
  select(id, cf_value) %>%
  droplevels %>%
  rename(country = cf_value) %>%
  left_join(projects, ., by = "id")
  

# Extract project id and business line information from custom_fields data frame
#  id:       project id
#  cf_value: business line
# In the LC database this is the relevant id - custom fields mapping:
#   15: Business line
projects <- filter(custom_fields, cf_id == 15) %>%
  select(id, cf_value) %>%
  droplevels %>%
  rename(business_line = cf_value) %>%
  left_join(projects, ., by = "id")



```

First, we need to identify customer names which indicate internal projects.

```{r, results='asis'}

proj_per_cust <- projects %>% count(customer) %>% arrange(customer)

print(xtable(proj_per_cust, 
             caption = "<b>Table 1:</b> Number of projects per customer"), type = 'html', include.rownames = FALSE)

```

Based on the analysis of the table above we construct a regular expression which is used to flag internal projects accordingly. 


```{r}

reg_ex <- '^all$|^ALL$|^All$|All Clients|Annesh|Annika|^Any$|ARIS Internal|ARIS User Group DACH|
Corporate Marketing|CustomerTemplate|Customer Name|^GCS|^gcs|^IBO|^IDS|^[iI]n-[Hh]ouse|
^[iI]nternal|itCampus|^Mathias|[Pp]lanio|^P[p]resales|^Product Marketing|RnD|
rnd|^SAG|^Self$|^Software AG|software ag|^SoftwareAG|^Solution Book|^test|^Test|various'

projects %<>% mutate(
  type = ifelse(grepl(reg_ex, customer), 'internal', 'external')
  )


```

This classification gives us the following intermediate result for all `r dim(projects)[1]` LabCase projects:

```{r}

table(projects$type)

with(projects, table(business_line, type))

```


## Results

In this section we will summarize the pre-processed data to create the desired bar plots. First, we will process the data and use the results as input for creating the plotting objecs before we acutally plot them.

```{r}
proj_by_year <- projects %>% mutate(
  year = year(created_on)
  ) %>% group_by(year, type) %>%
  summarize(
    n = n()
    ) 

g_proj_by_year <- ggplot(proj_by_year, aes(as.character(year), n, fill = type)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  geom_text(aes(label = n), position = position_dodge(.9), size = 4, 
            vjust = -0.3) +
  ggtitle('Number of created LabCase projects per year\n(focus on all business lines)') +
  xlab('Year of creation') +
  ylab('Number of projects') +
   scale_fill_brewer(palette = 'Set1') +
  
  theme(plot.title = element_text(size = 15),
        axis.title = element_text(size = 13),
        axis.text = element_text(size = 11)) +
  labs(fill = "Project type") +
   ylim(0, max(proj_by_year$n) * 1.05) 

```

```{r}

proj_by_year_gcs <- projects %>% filter(business_line %in% c('GCS', 'itCampus', 'IDS')) %>% mutate(
  year = year(created_on)
  ) %>% group_by(year, type) %>%
  summarize(
    n = n()
    ) 

g_proj_by_year_gcs <- ggplot(proj_by_year_gcs, aes(as.character(year), n, fill = type)) +
  geom_bar(stat = 'identity', position = position_dodge()) +
  geom_text(aes(label = n), position = position_dodge(.9), size = 4, 
            vjust = -0.3) +
  ggtitle('Number of created LabCase projects per year\n(focus on GCS including IDS and itCampus)') +
  xlab('Year of creation') +
  ylab('Number of projects') +
   scale_fill_brewer(palette = 'Set1') +
  
  theme(plot.title = element_text(size = 15),
        axis.title = element_text(size = 13),
        axis.text = element_text(size = 11)) +
  labs(fill = "Project type") +
   ylim(0, max(proj_by_year$n) * 1.05) 

```




```{r}




proj_by_year_qrt <- projects %>% mutate(
  year = year(created_on),
  quarter = quarters(created_on)
  ) %>% group_by(year, quarter, type) %>% 
  summarize(
    n = n()
    ) 
  
g_proj_by_year_qrt <- ggplot(proj_by_year_qrt, aes(quarter, n, fill = type)) + 
  geom_bar(stat = 'identity', position = position_dodge()) +
  geom_text(aes(label = n), position = position_dodge(.9), size = 4, vjust = -0.3) +
  facet_wrap(~ year ) +
  ggtitle('Number of created LabCase projects per year\n(quarterly focus on all business lines)') +
  xlab('Quarter of creation') +
  ylab('Number of projects') +
  scale_fill_brewer(palette = 'Set1') +
  theme(plot.title = element_text(size = 15),
        axis.title = element_text(size = 13),
        axis.text = element_text(size = 11),
        strip.text = element_text(size = 13)) +
  labs(fill = "Project type") +
   ylim(0, max(proj_by_year_qrt$n) * 1.05) 





```

```{r}


proj_by_year_qrt_gcs <- projects %>% filter(business_line %in% c('GCS', 'IDS', 'itCampus')) %>% mutate(
  year = year(created_on),
  quarter = quarters(created_on)
  ) %>% group_by(year, quarter, type) %>% 
  summarize(
    n = n()
    ) 
  
g_proj_by_year_qrt_gcs <- ggplot(proj_by_year_qrt_gcs, aes(quarter, n, fill = type)) + 
  geom_bar(stat = 'identity', position = position_dodge()) +
  geom_text(aes(label = n), position = position_dodge(.9), size = 4, vjust = -0.3) +
  facet_wrap(~ year ) +
  ggtitle('Number of created LabCase projects per year\n(quarterly focus on GCS including IDS and itCampus)') +
  xlab('Quarter of creation') +
  ylab('Number of projects') +
  scale_fill_brewer(palette = 'Set1') +
  theme(plot.title = element_text(size = 15),
        axis.title = element_text(size = 13),
        axis.text = element_text(size = 11),
        strip.text = element_text(size = 13)) +
  labs(fill = "Project type") +
   ylim(0, max(proj_by_year_qrt_gcs$n) * 1.05) 

```


```{r fig.width=8, fig.height=6, warning=FALSE, message=FALSE}

g_proj_by_year

```

```{r fig.width=8, fig.height=6, warning=FALSE, message=FALSE}

g_proj_by_year_gcs

```

```{r fig.width=10, fig.height=7, warning=FALSE, message=FALSE}

g_proj_by_year_qrt

```

```{r fig.width=10, fig.height=7, warning=FALSE, message=FALSE}

g_proj_by_year_qrt_gcs

```









