LabCase Global Report
========================================================

Data as of  `r as.character(date.of.extraction)`

```{r echo=FALSE}
library(lubridate)
library(ggplot2)
library(grid)
library(xtable)

source('../processedData/processedDataDump.R')
```

### General Information

```{r echo=FALSE, comment=NA }
paste('Data as of', date.of.extraction, sep=" ")

paste('Total number of projects:', dim(projects.df)[1], sep=" ")

paste('Total number of users:', users.dim[1], sep=" ")

paste('Number of SAG users:', sum(suffix.sag.df$Freq), sep=" ")

paste('Number of external users:', sum(suffix.external.df$Freq), sep=" ")

summary(projects.df$member_count, digits=3)

paste('Total number of Issues created in projects:',
          sum(projects.df$issue_count, na.rm=TRUE), sep=" ")

summary(projects.df$issue_count, digits=2)
```



### Project distribution 

This secion provides information about the project distribution among countries and among SAG departments. Examples how to interpret the figures:

* The left figure shows that `r subset(proj.created.by.country.df, Var1 == 'US', Freq)` projects were created in the United States alone
* On the right you can see that the GCS department is responsible for the creation of `r subset(proj.created.by.department.df, Var1 == 'GCS', Freq)` projects

```{r echo=FALSE, fig.width=10, fig.height=9}
# Create country ~ projects bar chart plot
# Exclude NAs
proj.created.by.country.df <- subset(proj.created.by.country.df,
                                        Var1 != '<NA>')

# Reorder so that the order in the barchart is flipped
proj.created.by.country.df <- transform(proj.created.by.country.df,
                                        Var1 = reorder(Var1,Freq))
g.countries <- ggplot(proj.created.by.country.df, aes(x=Var1, y=Freq)) +
  geom_bar(stat='identity', fill='#3182BD') +
  geom_text(aes(label=Freq), hjust=-0.1, size=4) +
  ggtitle('Number of projects\n per country') +
  ylim(0, max(proj.created.by.country.df$Freq) * 1.06) +
  xlab('Countries') +
  ylab('Number of projects') +
  theme(plot.title = element_text(size=rel(1.1)),
        axis.title = element_text(size=12),
        axis.text = element_text(size=10)) +
  coord_flip() 


# Create 'Department ~ projects bar chart plot
# Exclude NAs
proj.created.by.department.df <- subset(proj.created.by.department.df,
                                            Var1 != '<NA>')
# Reorder so that the order in the barchart is flipped
proj.created.by.department.df <- transform(proj.created.by.department.df,
                                               Var1 = reorder(Var1, Freq))
    
g.departments <- ggplot(proj.created.by.department.df, aes(x=Var1, y=Freq)) +
  geom_bar(stat='identity', fill='#3182BD') +
  geom_text(aes(label=Freq), hjust=-0.1, color='black', size=4) +
  ggtitle('Number of projects\n per department') +
  ylim(0, max(proj.created.by.department.df$Freq) * 1.08) +
  xlab('Departments') +
  ylab('Number of projects') +
  theme(plot.title = element_text(size=rel(1.1)),
        axis.title = element_text(size=12),
        axis.text = element_text(size=10)) +
  coord_flip() 


# Layout plots side-by-side on a 2-row-2-column grid
grid.newpage()
# Push viewport to graphic device
pushViewport(viewport(layout = grid.layout(2, 2, widths = c(0.5, 0.5))))
print(g.countries, vp = viewport(layout.pos.row = 1:2, layout.pos.col = 1))
print(g.departments, vp = viewport(layout.pos.row = 1, layout.pos.col = 2))
```


### Project growth

This section gives you an overview about projects created within different time spans. 
Our main focus lies on the following three periods:
* The last seven days
* Quarters of the current year
* Years since LabCase started its service


```{r echo=FALSE, fig.width=10, fig.height=8}
# Create time series plot for projects created in last 7 days
g.last.7.days <- ggplot(proj.created.in.last.7.days.df, 
                        aes(x=proj.created.in.last.7.days, y=Freq, group=1)) + 
                        geom_line(colour='#3182BD', size=1) +
                        geom_point(size=7, shape=21, fill='white') +
                        geom_text(aes(label=Freq), size=4) +
                        ggtitle(paste0(year(date.of.extraction), ': ',
                                'Number of created projects\n in the last 7 days per day (',
                                sum(proj.created.in.last.7.days.df$Freq),
                                ' overall)')) +
                        ylim(0, max(proj.created.in.last.7.days.df$Freq) * 1.02) +
                        xlab('Day of creation') +
                        ylab('Number of projects') +
                        theme(plot.title = element_text(size=rel(1.1)),
                              axis.title = element_text(size=12),
                              axis.text = element_text(size=10),
                              axis.text.x = element_text(angle=30, hjust=1, vjust=1))


# Create projects ~ quarters of current year bar chart
# Reorder so that the order in the barchart is flipped
g.quarters <- ggplot(proj.created.by.quarter.df, aes(x=proj.of.current.year, y=Freq)) +
                     geom_bar(width=.5, stat='identity', fill='#3182BD') +
                     geom_text(aes(label = Freq), vjust=-0.3, size=4) +
                     ggtitle(paste0(year(date.of.extraction), ': ',
                                    'Number of created projects\n per quarter')) +
                     ylim(0, max(proj.created.by.quarter.df$Freq) * 1.03) +
                     xlab('Quarter of creation') +
                     ylab('Number of projects') +
                     theme(plot.title = element_text(size=rel(1.1)),
                           axis.title = element_text(size=12),
                           axis.text = element_text(size=10)) 
  

#Create projects ~ years  bar chart
# Reorder so that the order in the barchart is flipped
proj.created.by.year.df <- proj.created.by.year.df[order(proj.created.by.year.df$Var1),]

g.years <- ggplot(proj.created.by.year.df, aes(x=Var1, y=Freq)) + 
                     geom_bar(width=.5, stat='identity', fill='#3182BD') +
                     geom_text(aes(label=Freq), vjust=-0.3, size=4) +
                     ggtitle('Number of created projects\n per year') +
                     ylim(0, max(proj.created.by.year.df$Freq) * 1.03) +
                     xlab('Year of creation') +
                     ylab('Number of projects') +
                     theme(plot.title = element_text(size=rel(1.1)),
                           axis.title = element_text(size=12),
                           axis.text = element_text(size=10))
                    
  



# Layout plots side-by-side on a 2-row-2-column grid
grid.newpage()
# Push viewport to graphic device
pushViewport(viewport(layout = grid.layout(2, 2)))

print(g.last.7.days, vp = viewport(layout.pos.row = 1, layout.pos.col = 1))
print(g.quarters, vp = viewport(layout.pos.row = 1, layout.pos.col = 2))
print(g.years, vp = viewport(layout.pos.row = 2, layout.pos.col = 1))




```




```{r echo=FALSE, results='asis'}
print(xtable(proj.created.by.country.df,caption="Projects per country"), type='html', html.table.attributes = "border = '1'")

```

  
  
  
  
 




