LabCase Global Report
========================================================

Data as of  `r as.character(date.of.extraction)`

```{r echo=FALSE}
library(ggplot2)
library(xtable)

source('../processedData/processedDataDump.R')
```

### General Information

```{r echo=FALSE, comment=NA }
paste('Data as of', date.of.extraction, sep=" ")

paste('Total number of projects:', dim(projects.df)[1], sep=" ")

paste('Total number of users:', users.dim[1], sep=" ")

paste('Number of SAG users:', sum(suffix.sag.df$Freq), sep=" ")

paste('Number of external users:', sum(suffix.external.df$Freq), sep=" ")

summary(projects.df$member_count, digits=3)

paste('Total number of Issues created in projects:',
          sum(projects.df$issue_count, na.rm=TRUE), sep=" ")

summary(projects.df$issue_count, digits=2)
```



### Project distribution 

This secion provides information about  the project distribution among countries and among SAG departments. For instance, the left figure shows that `r subset(proj.created.by.country.df, Var1 == 'US', Freq)` projects were created in the United States alone. On the right you can see that the GCS department is responsible for the creation of `r subset(proj.created.by.department.df, Var1 == 'GCS', Freq)` projects. 

```{r echo=FALSE, fig.width=12, fig.height=9}
# Create country ~ projects bar chart plot
# Exclude NAs
proj.created.by.country.df <- subset(proj.created.by.country.df,
                                        Var1 != '<NA>')

# Reorder so that the order in the barchart is flipped
proj.created.by.country.df <- transform(proj.created.by.country.df,
                                        Var1 = reorder(Var1,Freq))
g.countries <- ggplot(proj.created.by.country.df, aes(x=Var1, y=Freq)) +
  geom_bar(stat='identity', fill='#3182BD') +
  geom_text(aes(label=Freq), hjust=-0.1, size=4) +
  ggtitle('Number of projects\n per country') +
  ylim(0, max(proj.created.by.country.df$Freq) * 1.06) +
  xlab('Countries') +
  ylab('Number of projects') +
  theme(plot.title = element_text(size=rel(1.3)),
        axis.title = element_text(size=14),
        axis.text = element_text(size=10)) +
  coord_flip() 


# Create 'Department ~ projects bar chart plot
# Exclude NAs
proj.created.by.department.df <- subset(proj.created.by.department.df,
                                            Var1 != '<NA>')
# Reorder so that the order in the barchart is flipped
proj.created.by.department.df <- transform(proj.created.by.department.df,
                                               Var1 = reorder(Var1, Freq))
    
g.departments <- ggplot(proj.created.by.department.df, aes(x=Var1, y=Freq)) +
  geom_bar(stat='identity', fill='#3182BD') +
  geom_text(aes(label=Freq), hjust=-0.1, color='black', size=4) +
  ggtitle('Number of projects\n per department') +
  ylim(0, max(proj.created.by.department.df$Freq) * 1.06) +
  xlab('Departments') +
  ylab('Number of projects') +
  theme(plot.title = element_text(size=rel(1.3)),
        axis.title = element_text(size=14),
        axis.text = element_text(size=10)) +
  coord_flip() 


# Layout plots side-by-side on a 2-column grid
grid.newpage()
# Push viewport to graphic device
pushViewport(viewport(layout = grid.layout(1, 2, widths=c(0.5,0.5))))
print(g.countries, vp = viewport(layout.pos.row = 1, layout.pos.col = 1))
print(g.departments, vp = viewport(layout.pos.row = 1, layout.pos.col = 2))
```


```{r echo=FALSE, results='asis'}
print(xtable(proj.created.by.country.df,caption="Projects per country"), type='html', html.table.attributes = "border = '1'")

```

  
  
  
  
 




