# LabCase Global Report


```{r echo=FALSE, warning=FALSE}
library(lubridate)
library(ggplot2)
library(grid)
library(RColorBrewer)
library(dplyr)
library(scales)

source('../processedData/processedDataDump.R')

# Avoid scientifc notation in inline code for bigger numbers
options(scipen = 1, digits = 2)

# Create project frequency table grouped by country
proj.created.by.country.df <- as.data.frame.table(sort(table(projects.df$country,
                                                             useNA = 'ifany'), 
                                                       decreasing = TRUE))

# Create project frequency table grouped by department
proj.created.by.department.df <- as.data.frame.table(sort(table(projects.df$business_line,
                                                                useNA = 'ifany'), 
                                                          decreasing=TRUE))

```

Data as of  **`r as.character(date.of.extraction)`**


## General Information

* **Total** number of **projects**: **`r dim(projects.df)[1]`**
* **Total** number of **users**: **`r users.dim[1]`**

**User summary**:
```{r echo=FALSE, comment=NA}
summary(projects.df$member_count, digits = 3)
```

**Issue summary**: 
```{r echo=FALSE, comment=NA}
summary(projects.df$issue_count, digits = 2)
```

* **Total** number of **issues** created in projects: **`r sum(projects.df$issue_count, na.rm=TRUE)`**

## Project distribution 

This section provides information about the project distribution among countries and among SAG departments. Examples how to interpret the figures:

* The left figure shows that `r subset(proj.created.by.country.df, Var1 == 'US', Freq)` projects were created in the United States alone
* On the right you can see that the GCS department is responsible for the creation of `r subset(proj.created.by.department.df, Var1 == 'GCS', Freq)` projects

```{r echo=FALSE, fig.height=10, fig.width=10}
# Create country ~ projects bar chart plot
# Exclude NAs
proj.created.by.country.df <- subset(proj.created.by.country.df,
                                     Var1 != '<NA>')

# Reorder so that the order in the barchart is flipped
proj.created.by.country.df <- transform(proj.created.by.country.df,
                                        Var1 = reorder(Var1,Freq))
g.countries <- ggplot(proj.created.by.country.df, aes(x = Var1, y = Freq)) +
  geom_bar(stat = 'identity', fill = '#3182BD') +
  geom_text(aes(label = Freq), hjust = -0.1, size = 4) +
  ggtitle('Number of projects\n per country') +
  ylim(0, max(proj.created.by.country.df$Freq) * 1.06) +
  xlab('Countries') +
  ylab('Number of projects') +
  theme(plot.title = element_text(size = rel(1.1)),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10)) +
  coord_flip() 


# Create 'Department ~ projects bar chart plot
# Exclude NAs
proj.created.by.department.df <- subset(proj.created.by.department.df,
                                        Var1 != '<NA>')
# Reorder so that the order in the barchart is flipped
proj.created.by.department.df <- transform(proj.created.by.department.df,
                                           Var1 = reorder(Var1, Freq))
    
g.departments <- ggplot(proj.created.by.department.df, aes(x = Var1, y = Freq)) +
  geom_bar(stat = 'identity', fill = '#3182BD') +
  geom_text(aes(label = Freq), hjust = -0.1, color = 'black', size = 4) +
  ggtitle('Number of projects\n per department') +
  ylim(0, max(proj.created.by.department.df$Freq) * 1.08) +
  xlab('Departments') +
  ylab('Number of projects') +
  theme(plot.title = element_text(size = rel(1.1)),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10)) +
  coord_flip() 


# Layout plots side-by-side on a 2-row-2-column grid
grid.newpage()
# Push viewport to graphic device
pushViewport(viewport(layout = grid.layout(2, 2, widths = c(0.5, 0.5))))
print(g.countries, vp = viewport(layout.pos.row = 1:2, layout.pos.col = 1))
print(g.departments, vp = viewport(layout.pos.row = 1, layout.pos.col = 2))
```


## Project growth

This section gives you an overview about projects created within different time spans. 
Our main focus lies on the following three periods:
* The last seven days
* Quarters of the current year
* Years since LabCase started its service


```{r echo=FALSE, fig.width=12, fig.height=10}

proj.created.in.last.7.days.df <- mutate(proj.created.in.last.7.days.df,
                                         created_on = as.Date(created_on),
) %>%
  group_by(created_on, business_line) %>%
  summarise(
    numb_of_proj = n()
  ) %>%
  mutate(
    label_y = cumsum(numb_of_proj) 
  )

g.last.7.days <- ggplot(proj.created.in.last.7.days.df, aes(created_on, numb_of_proj)) +
  stat_summary(fun.y = sum, geom = 'text', aes(label = ..y..), vjust = -0.3, 
               size = 4) +
  geom_bar(stat = 'identity', width = 0.8, aes(fill = business_line)) +
  geom_text(aes(y = label_y, label = numb_of_proj), color = 'white', 
            vjust = 1.3, size = 4) +
  ggtitle(paste0(year(date.of.extraction), ': ',
                 'Number of created projects\n in the last 7 days per day (',
                 sum(proj.created.in.last.7.days.df$numb_of_proj),
                 ' overall)')) +
  xlab('Day of creation') +
  ylab('Number of projects') +
  theme(plot.title = element_text(size = rel(1.1)),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.text.x = element_text(angle = 30, hjust = 1, 
                                   vjust = 1)) +
  scale_x_date(
    breaks = '1 day', 
    limits = c(as.Date(date.of.extraction) - days(6), as.Date(date.of.extraction)), 
    labels = date_format("%d-%b"),
    expand = c(0,0.6)
  ) + 
  scale_fill_brewer(palette = 'Paired') + 
  labs(fill = 'Business line') +
  ylim(0, max(proj.created.in.last.7.days.df$label_y) * 1.05)


# Create projects ~ quarters of current year bar chart
# Reorder so that the order in the barchart is flipped
g.quarters <- ggplot(proj.created.by.quarter.df, aes(x = proj.of.current.year, 
                                                     y = Freq)) +
                     geom_bar(width = .5, stat = 'identity', fill = '#3182BD') +
                     geom_text(aes(label = Freq), vjust = -0.3, size = 4) +
                     ggtitle(paste0(year(date.of.extraction), ': ',
                                    'Number of created projects\n per quarter')) +
                     ylim(0, max(proj.created.by.quarter.df$Freq) * 1.03) +
                     xlab('Quarter of creation') +
                     ylab('Number of projects') +
                     theme(plot.title = element_text(size = rel(1.1)),
                           axis.title = element_text(size = 12),
                           axis.text = element_text(size = 10)) 
  

#Create projects ~ years  bar chart
# Reorder so that the order in the barchart is flipped
proj.created.by.year.df <- proj.created.by.year.df[order(proj.created.by.year.df$Var1),]

g.years <- ggplot(proj.created.by.year.df, aes(x = Var1, y = Freq)) + 
                     geom_bar(width = .5, stat  ='identity', fill = '#3182BD') +
                     geom_text(aes(label  =Freq), vjust = -0.3, size = 4) +
                     ggtitle('Number of created projects\n per year') +
                     ylim(0, max(proj.created.by.year.df$Freq) * 1.03) +
                     xlab('Year of creation') +
                     ylab('Number of projects') +
                     theme(plot.title = element_text(size = rel(1.1)),
                           axis.title = element_text(size = 12),
                           axis.text = element_text(size  =10))
                    
  



# Layout plots side-by-side on a 2-row-2-column grid
grid.newpage()
# Push viewport to graphic device
pushViewport(viewport(layout = grid.layout(2, 2)))

print(g.last.7.days, vp = viewport(layout.pos.row = 1, layout.pos.col = 1))
print(g.quarters, vp = viewport(layout.pos.row = 1, layout.pos.col = 2))
print(g.years, vp = viewport(layout.pos.row = 2, layout.pos.col = 1))
```





## User distribution

This section shows the distribution of LabCase users clustered by Software AG employees and external users (clients, partners):
* **Total** number of users: **`r users.dim[1]`**
* Number of **SAG** users: **`r sum(suffix.sag.df$Freq)`**
* Number of **external** users: **`r sum(suffix.external.df$Freq)`**


```{r echo=FALSE, fig.height=11, fig.width=12}

# Reorder so that the order in the barchart is flipped
suffix.sag.df <- transform(suffix.sag.df, 
                           suffix.sag = reorder(suffix.sag, Freq))

g.sag.users <- ggplot(suffix.sag.df, aes(x = suffix.sag, y  =Freq)) + 
                 geom_bar(stat = 'identity', fill = '#3182BD') +
                 geom_text(aes(label = Freq), hjust = -0.2, color = 'black', 
                           size = 4) +
                 ylim(0, max(suffix.sag.df$Freq) * 1.07) +
                 xlab('SAG unit') +
                 ggtitle('Number of active SAG users per unit') +
                 ylab('Number of users') +
                 theme(plot.title = element_text(size = rel(1.1)),
                      axis.title = element_text(size = 12),
                      axis.text = element_text(size = 10)) +
                coord_flip()

# Reorder so that the order in the barchart is flipped
suffix.external.df <- subset(suffix.external.df, Freq > 2)
suffix.external.df <- transform(suffix.external.df,
                                suffix.external = reorder(suffix.external, Freq))
    
g.external.users <- ggplot(suffix.external.df, aes(x = suffix.external, y = Freq)) +
                      geom_bar(stat = 'identity', fill = '#3182BD') +
                      geom_text(aes(label = Freq), hjust = -0.2, 
                                color = 'black', size = 4) +
                       ylim(0, max(suffix.external.df$Freq) * 1.03) +
                      xlab('Customers') +
                      ylab('Number of users') +
                      ggtitle('Customers with more than 2 active users') +
                      theme(plot.title = element_text(size = rel(1.1)),
                            axis.title = element_text(size = 12),
                            axis.text = element_text(size = 10)) +
                      coord_flip()


    

# Layout plots side-by-side on a 2-row-2-column grid
grid.newpage()
# Push viewport to graphic device
pushViewport(viewport(layout = grid.layout(2, 2)))

print(g.sag.users, vp = viewport(layout.pos.row = 1, layout.pos.col = 1))
print(g.external.users, vp = viewport(layout.pos.row = 1:2, layout.pos.col = 2))
```


## User activity 

This section shows the activity of the **`r users.dim[1]` registered users** within serveral defined time intervals based on their login behavior on the LabCase web front-end.

* Users active **in last 7 days:** **`r user.activity.df$active.obs[user.activity.df$interval.type == '7.day.interval']`**
* Users active **in last 14 days:** **`r user.activity.df$active.obs[user.activity.df$interval.type == '14.days.interval']`**
* Users active **in last 30 days:** **`r user.activity.df$active.obs[user.activity.df$interval.type == '30.day.interval']`**
* Users active **in last 60 days:** **`r user.activity.df$active.obs[user.activity.df$interval.type == '60.day.interval']`**
* Users active **in last 12 months:** **`r user.activity.df$active.obs[user.activity.df$interval.type == '12.months.interval']`**

*Note: We are only tracking user activity based on user logins via the LabCase web front-end. We are not taking into account users interacting with LabCase via a WebDAV client, a Subversion client or a Git client. In addition, the LabCase autologin attribute was set to 7 days. Therefore, the overall user activity in the 'last 7 days'-interval is approximately 20-30% higher than shown by the data above.*


## Disk space usage

This section provides information about the current disk space usage of projects hosted in LabCase. In general, LabCase projects can use two separate storage locations:
* The Assets section (Alfresco)
* The Repository section (Subversion and Git repositories)

The current **overall disk space usage** breakdown is as follows:

* **Total** disk space usage: **`r round(sum(projects.df$project_size, projects.df$repo_diskspace, na.rm=TRUE)/1024, digits=2)`** GB
* Total **Alfresco** disk space usage: **`r round(sum(projects.df$project_size, na.rm=TRUE)/1024, digits=2)`** GB
* Total **repository** disk space usage: **`r round(sum(projects.df$repo_diskspace, na.rm=TRUE)/1024, digits=2)`** GB


**Alfresco** disk space **summary** (in MB): 
```{r echo=FALSE, comment=NA}
summary(projects.df$project_size)
```
**Repository** disk space **summary** (in MB):
```{r echo=FALSE, comment=NA}
summary(projects.df$repo_diskspace)
```

```{r echo=FALSE, fig.height=10, fig.width=8}

# Change order of factor levels in origin column so that 'Alfresco' will get
# assigened the blue color of the ColorBrewer 'Set1' below
diskusage.per.project.df$origin <- factor(diskusage.per.project.df$origin,
                                          levels = c('Repository', 'Alfresco'))

 g <- ggplot(diskusage.per.project.df, aes(x = identifier, y = diskspace,
                                              fill = origin)) +
      geom_bar(stat = 'identity') +
      scale_fill_brewer(palette = 'Set1') +
      ggtitle(paste('Projects consuming more than 1GB of total disk space ',
                    '(', dim(diskusage.per.project.df)[1]/2, ' overall)',
                    sep='')) +
      ylim(0, max(diskusage.per.project.df$diskspace) * 1.02) +
      xlab('Project identifier') +
      ylab('Total disk space usage (MB)') +
      coord_flip() +
      theme(plot.title = element_text(size = rel(1.1)),
            axis.title = element_text(size = 12),
            axis.text = element_text(size = 10))
g
```


## Project templates

This section is dedicated to the project template feature. Below you will see:
* How many project templates are available globally
* The name of each created template
* The number of projects which were instantiated based on each template

**Number of available project templates**: `r dim(template.usage.df)[1]`

```{r echo=FALSE, fig.height=5}

# Reorder so that the order in the barchart is flipped
template.usage.df <- transform(template.usage.df, name=reorder(name, freq))
    
g <- ggplot(template.usage.df, aes(x = name, y = freq)) +
      geom_bar(stat = 'identity', fill = '#3182BD') +
      geom_text(aes(label = freq), hjust = -0.1, size  =4) +
      ylim(0, max(template.usage.df$freq) * 1.02) +
      xlab('Template name') +
      ylab('Number of instances') +
      ggtitle('Number of instantiated projects per template') +
      coord_flip() +
      theme(plot.title = element_text(size = rel(1.1)),
            axis.title = element_text(size = 12),
            axis.text = element_text(size = 10))
g
```